### 2025-02-12 short/sections/summary.tex
Update summary.tex

\textcolor{black}{My research, which initially focused on comparative politics and government, particularly cabinets, political regimes and civil services, has now expanded to explore the emerging field of digital governance and other policy domains. My work has appeared in {\itshape Social Science Computer Review}, {\itshape World Development}, {\itshape Government and Opposition}, {\itshape The International Journal of Press/Politics}, {\itshape The British Journal of Politics and International Relations} and elsewhere.}

>>>>

\textcolor{black}{From an earlier focus on cabinets and civil service, I have developed an active research agenda on how emerging technologies ---including AI--- shape policymaking and the organisation of bureaucracies. My work has appeared in {\itshape Social Science Computer Review}, {\itshape World Development}, {\itshape Government and Opposition}, {\itshape The International Journal of Press/Politics}, {\itshape The British Journal of Politics and International Relations} and elsewhere.}
